Revisiting some definitions with common examples from Gregorian calendar

### 2019-12-05 CyclicGran.Rmd
demystifying definitions using day and month example

---
title: Revisiting some definitions with examples from Gregorian calendar
author: Sayani Gupta
branding: FALSE
fontfamily: mathpazo
output: pdf_document
---

@@

Thus,  to obtain $month(13)$ in terms of days we can either use \autoref{def:periodical} or \autoref{eq:eq4}
\begin{equation}
\begin{split}
month(13) & =  month (1 + 12)\\
 & = \bigcup_{i \in S_1} day(i + 365) \quad since \quad month(1) =  \bigcup_{i \in S_1}day(i), \quad S_1 = {31, 32, \dots, 58}\\
 & = day(31 + 365)\bigcup day(32 + 365)\bigcup day(58 + 365)\\
\end{split}
\end{equation}

@@

A **circular** granularity can be defined using modular arithmetic due to its irregular mapping with the bottom granularity. They are formed with linear granularities, one of which "groups periodically into" the other.

@@

\begin{equation} \label{eq:eq2}
C_{B, G}(z) = {L}(z\mod k(B,G)) \quad \forall z \in \mathbb{Z}^+
\end{equation}
where,
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity G with regular mapping, 
{L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (k-1)}$,
and k(B,G) is the number of granules of B in each granule of G.
\end{definition}

@@

A **quasi-circular** granularity can not be defined using modular arithmetic due to its irregular mapping with the bottom granularity. However, they are still formed with linear granularities, one of which "groups periodically into" the other. We will take the example of days and months to illustrate the notion of "groups periodically into" and "quasi-circular" granularities.

Till now, we saw how the formal definitions of "groups periodically into" can be seen through the example of (day, month). Now, we shall discuss how some quasi-circular granularity can be obtained. \autoref{fig:quasi-circular-explain} shows that index set 34 should correspond to L(3) which is "4th-day-of-month", that of 60 should correspond to L(1), which is "2nd-day-of-month" and 334 should correspond to L(0), which is "1st-day-of-month". Now, quasi-circular granularities can be defined as follows to obtain these labels:

@@

@@

\begin{equation}\label{eq:eq4}
\begin{split}
A_{B, G''}(z) & = L(1), z \in T_q\\
     & = L(0), z \not\in T_q\\
\end{split}
\end{equation}
where,  
$z$ denotes the index set (index of $B$),
$T_q$ are the sets of indices of $B$ describing $G''(q)$ such that $G''(q) = \bigcup_{z \in T_q}BG(z)$,$T_q = 0$ for $q \epsilon Z_{<0}$.
\end{definition}

Discussion: Aperiodic time granularities map a time index to a categorical variable containing binary values. It takes the value 1 whenever the time index coincides with the events in context (e.g. public or school holiday) and 0 when it does not. Here, 1 and 0 are proxies to denote the binary categorization and can be replaced with a logical vector. An example of aperiodic granularity can be one that relates a bottom granularity ($BG$) and linear granularity ($G''$) such that $BG \trianglelefteq G''$, $BG \not\preceq G$ and $BG$ is not periodic or quasi-periodic with respect to $G''$, as shown in \autoref{fig:aperiodic}.

```{r aperiodic, echo=FALSE,out.width = "100%",fig.cap="Relating aperiodic granularity and bottom linear granularity "}
knitr::include_graphics("Figs/aperiodic.png")

>>>>

---
title: Revisiting some definitions with common examples from Gregorian calendar
author: Sayani Gupta
branding: FALSE
fontfamily: mathpazo
output: pdf_document
---

@@

Thus,  to obtain $month(13)$ in terms of days we can either use Definition \autoref{def:periodical} or \autoref{eq:eq4}
\begin{equation}
\begin{split}
month(13) & =  month (1 + 12)\\
 & = \bigcup_{i \in S_1} day(i + 365) \quad since \quad month(1) =  \bigcup_{i \in S_1}day(i), \quad S_1 = {31, 32, \dots, 58}\\
 & = day(31 + 365)\bigcup day(32 + 365)\bigcup day(58 + 365)\\
\end{split}
\end{equation}

@@

A **circular** granularity can be defined using modular arithmetic due to its regular mapping with the bottom granularity. They are formed with linear granularities, one of which "groups periodically into" the other. In the following definition, we would assume that bottom granularity $B$ groups periodically into $G$ and number of granules of $B$ in each granule of $G$ is constant. Thus, if $P$ and $R$  have the meaning of the period of the grouping $(B, G)$ and the number of granules of $G$ in each of these periods, then for circular granularity, $P/R \in \mathbb{Z}^+$. Also, since each granule of $G$ has same number of granules of $B$, $R$ can be taken to be $1$ and $P$ can be interpreted as the number of granules of B in any granule of G.

@@

\begin{equation} \label{eq:eq2}
\begin{split}
C_{B, G}(z) & = {L}(z\mod P) \quad \forall z \in \mathbb{Z}^+ \\
\end{split}
\end{equation}
where,
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity G with regular mapping, 
{L} is a label mapping that defines an unique label for each index $l \in {0,1,\dots, (P-1)}$,
and P is the number of granules of B in each granule of G.
\end{definition}

@@

A **quasi-circular** granularity can not be defined using modular arithmetic due to its irregular mapping with the bottom granularity. Here $P/R \not \in \mathbb{Z}^+$. However, they are still formed with linear granularities, one of which "groups periodically into" the other. We shall discuss an example of  quasi-circular granularity day-of-month in \autoref{fig:quasi-circular-explain}. The index 34 should correspond to L(3) which is "4th-day-of-month", that of 60 should correspond to L(1), which is "2nd-day-of-month" and 334 should correspond to L(0), which is "1st-day-of-month". Now, quasi-circular granularities can be defined as follows to obtain these labels:

@@

In \autoref{fig:quasi-circular-explain}, the label mapping L can be defined as $L: ({0,1,2, \dots, 31}) \longmapsto\ ({DOM_1, DOM_2, \dots, DOM_{31})}$ or $L: ({0,1,2, \dots, 31}) \longmapsto\ ({1, 2, \dots, 31)}$
depending on the context.

@@

\begin{equation}\label{eq:eq4}
\begin{split}
A_{B, G''}(z) & = L(1), \quad z \in T_q\\
     & = L(0), \quad z \not\in T_q\\
\end{split}
\end{equation}
where  
$z$ denotes the index set,
$T_q$ are the sets of indices of $B$ describing $G''(q)$ such that $$G''(q) = \bigcup_{z \in T_q}B(z)$$
\end{definition}

 Aperiodic time granularities map a time index to binary categories. It takes the value 1 whenever the time index coincides with the events in context (e.g. public or school holiday) and 0 when it does not. \autoref{fig:aperiodic} shows the linear granularity academic semester and days. Academic semesters are not periodic with respect to days. The label mapping L can be defined as $L: ({0,1}) \longmapsto\ ({On, Off)}$ or can be customised based on context.

```{r aperiodic, echo=FALSE,out.width = "100%",fig.cap=" Aperiodic granularity day-semester"}
knitr::include_graphics("Figs/academ-semester.png")
